---
title: "NHL Dashboard Graphs"
author: "Nick Sofianakos"
date: "2024-07-14"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(tidyquant)
library(pacman)
library(devtools)
library(ggforce)
library(plotly)
library(ggimage)
library(scales)
library(ggthemes)
library(RCurl)
centertitle <- theme(plot.title = element_text(hjust = 0.5))
centersub <- theme(plot.subtitle = element_text(hjust = 0.5))
```

Alright time to make some graphs now that packages are loaded in
```{r}
ASAS <- read_csv("AllStrengthsAllScoresCounts.csv")
NHL_Logos <- read_csv("nhl_logos.csv")
```

```{r}
AS_AllScores <- left_join(ASAS,NHL_Logos,
                           by= c("Team"= "espn_team_name"))
```
Selecting only espn_logo, xGA,xGF from the dataframe to avoid null values messing it up.
```{r}

viz1 <- AS_AllScores %>% 
  select(espn_logo,xGF,xGA) %>% 
  mutate(espn_logo=replace_na(espn_logo,"https://a.espncdn.com/i/teamlogos/nhl/500/stl.png"))
```


Making Graph: All Strengths, All Scores, xGF vs xGA
```{r}
mean_xGF <- mean(viz1$xGF, na.rm = TRUE)
mean_xGA <- mean(viz1$xGA, na.rm = TRUE)
asp <- 1.618
width<- 20


viz1 %>% 
  ggplot(aes(x=xGA,y=xGF,image=espn_logo))+
  geom_image(size=0.06, asp=asp)+
  labs(title= "NHL 2023-2024",
        subtitle = "xGF vs xGA (All Scores, All Strengths)",
        x= "xGA",
        y= "xGF",
        caption= "Data Source: Natural Stat Trick")+
   centertitle+
   centersub +
    geom_hline(yintercept = mean_xGF, color = "white", linetype = "dashed") +
  geom_vline(xintercept = mean_xGA, color = "white", linetype = "dashed") +
       annotate("text", x = 235, y = 225, 
                label = "Bad Offense/Good Defense", color="white") +
       annotate("text", x = 235, y = 290,
                label = "Good Offense/Good Defense", color="white") + 
       annotate("text", x = 280, y = 225,
                label = "Bad Offense/Bad Defense", color="white") + 
       annotate("text", x = 280, y = 290,
                label = "Good Offense/Bad Defense", color="white")+
  theme_minimal(base_family = "Arial") + # Use a minimal theme as the base
  theme(
    plot.background = element_rect(fill = "#282a36", color = NA),
    panel.background = element_rect(fill = "#282a36", color = NA),
    plot.title = element_text(color = "white", hjust = 0.5),
    plot.subtitle = element_text(color = "white", hjust = 0.5),
    plot.caption = element_text(color = "white"),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines

  )

```

Saving the plot Attempt better(WORKS GREAT!!!!!!)
```{r}
ggsave(filename = "nhl_2023_2024_ASAS.png", dpi=600, width = width, height = width/asp, units = "cm")
```

Now, we have successfully made an Expected Goals For vs Expected Goals Against plot for the 2023-24 regular season for All Scores and Strengths. Going to keep making the same graph but for different scores and strengths. 

2)All Strengths, and Tied

Load in the data
```{r}
AST <- read_csv("AllStrengthsTiedCounts.csv")
```

Merge with NHL Logo Data
```{r}
AS_Tied <- left_join(AST,NHL_Logos,
                           by= c("Team"= "espn_team_name"))
```

Select Team Logo, xGF, xGA
```{r}
viz2 <- AS_Tied %>% 
  select(espn_logo,xGF,xGA) %>% 
  mutate(espn_logo=replace_na(espn_logo,"https://a.espncdn.com/i/teamlogos/nhl/500/stl.png"))
```

Making the Graph: All Strengths, and Tied
```{r}
mean_xGF_ASTied <- mean(viz2$xGF, na.rm = TRUE)
mean_xGA_ASTied <- mean(viz2$xGA, na.rm = TRUE)
asp <- 1.618
width<- 20

#50 to 115 in both direction for limits
viz2 %>% 
  ggplot(aes(x=xGA,y=xGF,image=espn_logo))+
  geom_image(size=0.06, asp=asp)+
  labs(title= "NHL 2023-2024",
        subtitle = "xGF vs xGA (All Scores, Tied)",
        x= "xGA",
        y= "xGF",
        caption= "Data Source: Natural Stat Trick")+
   centertitle+
   centersub +
    geom_hline(yintercept = mean_xGF_ASTied, color = "white", linetype = "dashed") +
  geom_vline(xintercept = mean_xGA_ASTied, color = "white", linetype = "dashed") +
       annotate("text", x = 72, y = 62.5, 
                label = "Bad Offense/Good Defense", color="white") +
       annotate("text", x = 72, y = 110,
                label = "Good Offense/Good Defense", color="white") +
       annotate("text", x = 100, y = 62.5,
                label = "Bad Offense/Bad Defense", color="white") + 
       annotate("text", x = 100, y = 110,
                label = "Good Offense/Bad Defense", color="white")+
  theme_minimal(base_family = "Arial") + # Use a minimal theme as the base
  theme(
    plot.background = element_rect(fill = "#282a36", color = NA),
    panel.background = element_rect(fill = "#282a36", color = NA),
    plot.title = element_text(color = "white", hjust = 0.5),
    plot.subtitle = element_text(color = "white", hjust = 0.5),
    plot.caption = element_text(color = "white"),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines

  )
```
Saving the graph to a png
```{r}
ggsave(filename = "nhl_2023_2024_ASTied.png", dpi=600, width = width, height = width/asp, units = "cm")
```



3)All Strengths, and Leading

Load in the data
```{r}
ASL <- read_csv("AllStrengthsLeadingCounts.csv")
```

Merge with NHL Logo Data
```{r}
AS_Leading <- left_join(ASL,NHL_Logos,
                           by= c("Team"= "espn_team_name"))
```

Select Team Logo, xGF, xGA
```{r}
viz3 <- AS_Leading %>% 
  select(espn_logo,xGF,xGA) %>% 
  mutate(espn_logo=replace_na(espn_logo,"https://a.espncdn.com/i/teamlogos/nhl/500/stl.png"))
```

Making the Graph: All Strengths, and Tied
```{r}
mean_xGF_ASLeading <- mean(viz3$xGF, na.rm = TRUE)
mean_xGA_ASLeading <- mean(viz3$xGA, na.rm = TRUE)
asp <- 1.618
width<- 20

#50 to 115 in both direction for limits
viz3 %>% 
  ggplot(aes(x=xGA,y=xGF,image=espn_logo))+
  geom_image(size=0.06, asp=asp)+
  labs(title= "NHL 2023-2024",
        subtitle = "xGF vs xGA (All Scores, Leading)",
        x= "xGA",
        y= "xGF",
        caption= "Data Source: Natural Stat Trick")+
   centertitle+
   centersub +
    geom_hline(yintercept = mean_xGF_ASLeading, color = "white", linetype = "dashed") +
  geom_vline(xintercept = mean_xGA_ASLeading, color = "white", linetype = "dashed") +
       annotate("text", x = 72, y = 62.5, 
                label = "Bad Offense/Good Defense", color="white") +
       annotate("text", x = 72, y = 110,
                label = "Good Offense/Good Defense", color="white") +
       annotate("text", x = 100, y = 62.5,
                label = "Bad Offense/Bad Defense", color="white") + 
       annotate("text", x = 100, y = 110,
                label = "Good Offense/Bad Defense", color="white")+
  theme_minimal(base_family = "Arial") + # Use a minimal theme as the base
  theme(
    plot.background = element_rect(fill = "#282a36", color = NA),
    panel.background = element_rect(fill = "#282a36", color = NA),
    plot.title = element_text(color = "white", hjust = 0.5),
    plot.subtitle = element_text(color = "white", hjust = 0.5),
    plot.caption = element_text(color = "white"),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines

  )
```
Saving the graph to a png
```{r}
ggsave(filename = "nhl_2023_2024_ASLeading.png", dpi=600, width = width, height = width/asp, units = "cm")
```

4)All Strengths, and Trailing

Load in the data
```{r}
ASTrail <- read_csv("AllStrengthsTrailingCounts.csv")
```

Merge with NHL Logo Data
```{r}
AS_Trailing <- left_join(ASTrail,NHL_Logos,
                           by= c("Team"= "espn_team_name"))
```

Select Team Logo, xGF, xGA
```{r}
viz4 <- AS_Trailing %>% 
  select(espn_logo,xGF,xGA) %>% 
  mutate(espn_logo=replace_na(espn_logo,"https://a.espncdn.com/i/teamlogos/nhl/500/stl.png"))
```

Making the Graph: All Strengths, and Tied
```{r}
mean_xGF_ASTrailing <- mean(viz4$xGF, na.rm = TRUE)
mean_xGA_ASTrailing <- mean(viz4$xGA, na.rm = TRUE)
asp <- 1.618
width<- 20

#50 to 115 in both direction for limits
viz4 %>% 
  ggplot(aes(x=xGA,y=xGF,image=espn_logo))+
  geom_image(size=0.06, asp=asp)+
  labs(title= "NHL 2023-2024",
        subtitle = "xGF vs xGA (All Scores, Trailing)",
        x= "xGA",
        y= "xGF",
        caption= "Data Source: Natural Stat Trick")+
   centertitle+
   centersub +
    geom_hline(yintercept = mean_xGF_ASTrailing, color = "white", linetype = "dashed") +
  geom_vline(xintercept = mean_xGA_ASTrailing, color = "white", linetype = "dashed") +
       annotate("text", x = 66, y = 62.5, 
                label = "Bad Offense/Good Defense", color="white") +
       annotate("text", x = 66, y = 110,
                label = "Good Offense/Good Defense", color="white") +
       annotate("text", x = 108, y = 62.5,
                label = "Bad Offense/Bad Defense", color="white") + 
       annotate("text", x = 108, y = 110,
                label = "Good Offense/Bad Defense", color="white")+
  theme_minimal(base_family = "Arial") + # Use a minimal theme as the base
  theme(
    plot.background = element_rect(fill = "#282a36", color = NA),
    panel.background = element_rect(fill = "#282a36", color = NA),
    plot.title = element_text(color = "white", hjust = 0.5),
    plot.subtitle = element_text(color = "white", hjust = 0.5),
    plot.caption = element_text(color = "white"),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines

  )
```
Saving the graph to a png
```{r}
ggsave(filename = "nhl_2023_2024_ASTrailing.png", dpi=600, width = width, height = width/asp, units = "cm")
```


5)All Strengths, and Within One

Load in the data
```{r}
ASW1 <- read_csv("AllStrengthsWithinOneCounts.csv")
```

Merge with NHL Logo Data
```{r}
AS_Within1 <- left_join(ASW1,NHL_Logos,
                           by= c("Team"= "espn_team_name"))
```

Select Team Logo, xGF, xGA
```{r}
viz5 <- AS_Within1 %>% 
  select(espn_logo,xGF,xGA) %>% 
  mutate(espn_logo=replace_na(espn_logo,"https://a.espncdn.com/i/teamlogos/nhl/500/stl.png"))
```

Making the Graph: All Strengths, and Tied
```{r}
mean_xGF_ASW1 <- mean(viz5$xGF, na.rm = TRUE)
mean_xGA_ASW1 <- mean(viz5$xGA, na.rm = TRUE)
asp <- 1.618
width<- 20

#125 to 210 in both direction for limits
viz5 %>% 
  ggplot(aes(x=xGA,y=xGF,image=espn_logo))+
  geom_image(size=0.06, asp=asp)+
  labs(title= "NHL 2023-2024",
        subtitle = "xGF vs xGA (All Scores, Within One)",
        x= "xGA",
        y= "xGF",
        caption= "Data Source: Natural Stat Trick")+
   centertitle+
   centersub +
    geom_hline(yintercept = mean_xGF_ASW1, color = "white", linetype = "dashed") +
  geom_vline(xintercept = mean_xGA_ASW1, color = "white", linetype = "dashed") +
       annotate("text", x = 153, y = 120, 
                label = "Bad Offense/Good Defense", color="white") +
       annotate("text", x = 153, y = 200,
                label = "Good Offense/Good Defense", color="white") +
       annotate("text", x = 190, y = 120,
                label = "Bad Offense/Bad Defense", color="white") + 
       annotate("text", x = 190, y = 200,
                label = "Good Offense/Bad Defense", color="white")+
  theme_minimal(base_family = "Arial") + # Use a minimal theme as the base
  theme(
    plot.background = element_rect(fill = "#282a36", color = NA),
    panel.background = element_rect(fill = "#282a36", color = NA),
    plot.title = element_text(color = "white", hjust = 0.5),
    plot.subtitle = element_text(color = "white", hjust = 0.5),
    plot.caption = element_text(color = "white"),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines

  )
```

Saving the graph to a png
```{r}
ggsave(filename = "nhl_2023_2024_ASW1.png", dpi=600, width = width, height = width/asp, units = "cm")
```

6)All Strengths, and Up One

Load in the data
```{r}
ASU1 <- read_csv("AllStrengthsUpOneCounts.csv")
```

Merge with NHL Logo Data
```{r}
AS_Up1 <- left_join(ASU1,NHL_Logos,
                           by= c("Team"= "espn_team_name"))
```

Select Team Logo, xGF, xGA
```{r}
viz6 <- AS_Up1 %>% 
  select(espn_logo,xGF,xGA) %>% 
  mutate(espn_logo=replace_na(espn_logo,"https://a.espncdn.com/i/teamlogos/nhl/500/stl.png"))
```

Making the Graph: All Strengths, and Tied
```{r}
mean_xGF_ASU1 <- mean(viz6$xGF, na.rm = TRUE)
mean_xGA_ASU1 <- mean(viz6$xGA, na.rm = TRUE)
asp <- 1.618
width<- 20

#10 to 70 in both direction for limits
viz6 %>% 
  ggplot(aes(x=xGA,y=xGF,image=espn_logo))+
  geom_image(size=0.06, asp=asp)+
  labs(title= "NHL 2023-2024",
        subtitle = "xGF vs xGA (All Scores, Up One)",
        x= "xGA",
        y= "xGF",
        caption= "Data Source: Natural Stat Trick")+
   centertitle+
   centersub +
    geom_hline(yintercept = mean_xGF_ASU1, color = "white", linetype = "dashed") +
  geom_vline(xintercept = mean_xGA_ASU1, color = "white", linetype = "dashed") +
       annotate("text", x = 38, y = 25, 
                label = "Bad Offense/Good Defense", color="white") +
       annotate("text", x = 38, y = 58,
                label = "Good Offense/Good Defense", color="white") +
       annotate("text", x = 58, y = 25,
                label = "Bad Offense/Bad Defense", color="white") + 
       annotate("text", x = 58, y = 58,
                label = "Good Offense/Bad Defense", color="white")+
  theme_minimal(base_family = "Arial") + # Use a minimal theme as the base
  theme(
    plot.background = element_rect(fill = "#282a36", color = NA),
    panel.background = element_rect(fill = "#282a36", color = NA),
    plot.title = element_text(color = "white", hjust = 0.5),
    plot.subtitle = element_text(color = "white", hjust = 0.5),
    plot.caption = element_text(color = "white"),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines

  )
```
Saving the graph to a png
```{r}
ggsave(filename = "nhl_2023_2024_ASU1.png", dpi=600, width = width, height = width/asp, units = "cm")
```

7)All Strengths, and Down One

Load in the data
```{r}
ASD1 <- read_csv("AllStrengthsDownOneCounts.csv")
```

Merge with NHL Logo Data
```{r}
AS_Down1 <- left_join(ASD1,NHL_Logos,
                           by= c("Team"= "espn_team_name"))
```

Select Team Logo, xGF, xGA
```{r}
viz7 <- AS_Down1 %>% 
  select(espn_logo,xGF,xGA) %>% 
  mutate(espn_logo=replace_na(espn_logo,"https://a.espncdn.com/i/teamlogos/nhl/500/stl.png"))
```

Making the Graph: All Strengths, and Tied
```{r}
mean_xGF_ASD1 <- mean(viz7$xGF, na.rm = TRUE)
mean_xGA_ASD1 <- mean(viz7$xGA, na.rm = TRUE)
asp <- 1.618
width<- 20

#10 to 70 in both direction for limits
viz7 %>% 
  ggplot(aes(x=xGA,y=xGF,image=espn_logo))+
  geom_image(size=0.06, asp=asp)+
  labs(title= "NHL 2023-2024",
        subtitle = "xGF vs xGA (All Scores, Down One)",
        x= "xGA",
        y= "xGF",
        caption= "Data Source: Natural Stat Trick")+
   centertitle+
   centersub +
    geom_hline(yintercept = mean_xGF_ASD1, color = "white", linetype = "dashed") +
  geom_vline(xintercept = mean_xGA_ASD1, color = "white", linetype = "dashed") +
       annotate("text", x = 32, y = 25, 
                label = "Bad Offense/Good Defense", color="white") +
       annotate("text", x = 32, y = 58,
                label = "Good Offense/Good Defense", color="white") +
       annotate("text", x = 58, y = 25,
                label = "Bad Offense/Bad Defense", color="white") + 
       annotate("text", x = 58, y = 58,
                label = "Good Offense/Bad Defense", color="white")+
  theme_minimal(base_family = "Arial") + # Use a minimal theme as the base
  theme(
    plot.background = element_rect(fill = "#282a36", color = NA),
    panel.background = element_rect(fill = "#282a36", color = NA),
    plot.title = element_text(color = "white", hjust = 0.5),
    plot.subtitle = element_text(color = "white", hjust = 0.5),
    plot.caption = element_text(color = "white"),
    axis.title.x = element_text(color = "white"),
    axis.title.y = element_text(color = "white"),
    axis.text = element_text(color = "white"),
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank()  # Remove minor grid lines

  )
```

Saving the graph to a png
```{r}
ggsave(filename = "nhl_2023_2024_ASD1.png", dpi=600, width = width, height = width/asp, units = "cm")
```

8)Even Strength, and All Scores
9)Even Strength, and Tied
10)Even Strength, and Leading
11)Even Strength, and Trailing
12)Even Strength, and Within One
13)Even Strength, and Up One
14)Even Strength, and Down One

15)5v5, and All Scores 
16)5v5, and Tied 
17)5v5, and Leading 
18)5v5, and Trailing
19)5v5, and Within One
20)5v5, and Up One 
21)5v5, and Down One

22)Score and Venue adjusted 5v5, and All Scores 
23)Score and Venue adjusted 5v5, and Tied 
24)Score and Venue adjusted 5v5, and Leading 
25)Score and Venue adjusted 5v5, and Trailing
26)Score and Venue adjusted 5v5, and Within One
27)Score and Venue adjusted 5v5, and Up One 
28)Score and Venue adjusted 5v5, and Down One


